To measure the backend's performance under stress, load tests were conducted using Siege \cite{SIEGE}, an open-source HTTP/HTTPS benchmarking utility. The tests were configured to simulate 10 concurrent users making continuous requests over a 30-second period. All requests included a valid JWT to ensure the authentication middleware was also evaluated. Three key endpoints were selected to test different aspects of the backend:

\begin{compactitem}[\textbullet]
    \item \textbf{Root (\texttt{/}):} A baseline test to measure the raw request-handling speed of FastAPI.
    \item \textbf{Ollama Proxy (\texttt{/ollama/api/version}):} To measure the overhead introduced by proxying requests to the Ollama service.
    \item \textbf{FalkorDB Query (\texttt{/get-chat-history}):} To measure the latency of querying the graph database (with indexed identifiers), getting an example history of 6072 bytes.
\end{compactitem}

Endpoints interacting with the Supabase cloud \acs{api} were not tested due to bandwidth limitations. The results, summarized in Table~\ref{TAB:API_LOAD_TEST}, demonstrate that the backend is highly performant, capable of handling thousands of transactions per second with an average response time in the single-digit milliseconds.

\begin{table}[Load Test Results]{TAB:API_LOAD_TEST}{\acs{api} Load Test Results (10 concurrent users over 30s).}
    \centering
    \begin{tabular}{l r r r}
        \hline
        \textbf{Metric} & \textbf{Root (\texttt{/})} & \textbf{Ollama Proxy} & \textbf{FalkorDB Query} \\
        \hline\hline
        Transaction Rate (trans/sec) & 5620.67 & 2428.50 & 2964.35 \\
        Average Response Time (ms) & 1.75 & 4.08 & 3.34 \\
        Concurrency Rate & 9.84 & 9.91 & 9.89 \\
        Throughput (MB/sec) & 0.13 & 0.04 & 17.17 \\
        Successful Transactions & 170,194 & 74,555 & 89,879 \\
        Failed Transactions & 0 & 0 & 0 \\
        \hline
    \end{tabular}
\end{table}