\glsreset{llm}
\glsreset{sus}

While \acp{llm} have created new paradigms for human-computer interaction, their application in \acp{rs} presents significant research challenges. Traditional systems often fail to capture the nuances of user preferences, and the black-box nature of many models erodes user trust. There is a pressing need for \aclp{crs} that can dynamically elicit user preferences, build comprehensive user profiles, and provide transparent, explainable recommendations.

This Master's Thesis addresses these challenges by proposing and evaluating a novel hybrid framework for explainable conversational recommendation. The primary research objective is to investigate how a combination of conversational interaction, dynamic user profiling, and graph-based reasoning can lead to more effective, transparent, and user-centric recommendation experiences.

To this end, a hybrid \acl{crs} was designed and implemented. The system's core is a LlamaIndex workflow that orchestrates the conversational flow. During the interaction, the system dynamically constructs a user profile by capturing explicit and implicit preferences. This profile informs a hybrid recommendation strategy that leverages both a real-time, graph-based engine using \texttt{FalkorDB} for contextual and explainable recommendations, and a pre-trained expert model (\texttt{EASER}) for deep personalization. A key contribution is the use of graph reasoning techniques to generate natural language explanations that justify the system's suggestions. The platform was empirically evaluated through a usability study involving 11 participants to assess user satisfaction, task success, and perceived usability via the \ac{sus}.

The results are highly promising, indicating the viability of the proposed hybrid approach. The system achieved a \acs{sus} score of 92 out of 100, and qualitative feedback from users highlighted the intuitiveness of the conversational interaction and the relevance of the recommendations. This thesis contributes a validated framework for building explainable recommender agents, demonstrating that the integration of dynamic user profiling and graph-based explanation generation is a step towards creating more trustworthy and effective \aclp{rs}.

\keywords{Conversational Recommender System, Explainable AI, User Profiling, Large Language Models, Human-Computer Interaction, Graph-Based Recommendation, Usability Testing}
