\glsreset{llm}
\glsreset{api}
\glsreset{pwa}
\glsreset{ai}

The recent proliferation of \acp{llm} has catalyzed significant interest in the development of advanced conversational systems. However, integrating these models into scalable, robust, and user-friendly \acl{recsys} platforms remains a complex engineering challenge. Current solutions often lack an end-to-end framework that simplifies deployment and supports real-world scalability.

This Master's Thesis addresses this problem by detailing the design and implementation of a scalable and modular platform for the creation of hybrid conversational recommender agents. The primary objective is to develop a comprehensive, full-stack solution that automates the entire lifecycle of a conversational agent, from creation and data processing to deployment and user interaction.

The platform is designed using a containerized approach with Docker to ensure modularity, portability, and scalability. The backend is built upon the high-performance FastAPI framework, which exposes a RESTful \ac{api} to manage agents, process datasets, and handle conversational logic. For the frontend, a responsive and installable \ac{pwa} was developed using Next.js, providing an intuitive interface for users to manage their recommender agents and engage in conversations. The system's data layer leverages Supabase, a cloud-based relational database for storing agent and conversation metadata; and FalkorDB as a high-performance graph database to model the relationships between users and items, and to store chat histories. A key feature is the automated data processing pipeline that handles the ingestion, cleansing, and structuring of user-uploaded datasets.

The final result of this project is a fully functional, end-to-end platform that empowers users to seamlessly create, manage, and interact with personalized conversational recommender agents. The robust architecture prioritizes efficiency, scalability, and reproducibility, providing a solid foundation for future development and research at the intersection of conversational \acs{ai} and \acl{recsys}s.

\keywords{Conversational recommender system, large language models, full-stack development, scalable architecture, system design, graph databases, FastAPI, Next.js, Docker}
