Designing an effective \ac{ui} and \ac{ux} for \ac{llm}-powered applications presents unique challenges that differ from traditional web applications. The interaction model shifts from predictable, form-based inputs to fluid, open-ended conversations, which requires a more dynamic and responsive interface.

A key principle in conversational \acs{ui} design is managing user expectations and providing continuous feedback. Due to the potential latency of \ac{llm} responses, it is favorable to stream tokens to the user as they are generated. This creates an immediate sense of activity and reduces perceived wait times. Additionally, the \acs{ui} should clearly indicate the system's current state, for example, by showing when it is processing a request, retrieving information, or using an external tool. Beyond the conversational aspects, adhering to fundamental principles of modern web design is also important. This includes implementing a fully responsive design to ensure the platform is accessible and usable across a wide range of devices, from large desktop monitors to mobile phones. A responsive layout is critical for a \ac{pwa}, as it guarantees a consistent and high-quality experience regardless of the device from which the user accesses the application.

To achieve a polished and intuitive user experience, this project utilizes modern \acs{ui} component libraries. Specifically, it leverages \texttt{shadcn/ui} \cite{SHADCN-UI}, a collection of beautifully designed components, and \texttt{assistant-ui} \cite{ASSISTANT-UI}, a React library specifically tailored for building \acs{ai} chat interfaces. These tools provide the necessary building blocks to implement features like streaming responses, displaying conversation history, and handling complex user interactions, ensuring the final application is both functional and visually appealing.