The primary objective of this Master's Thesis is the design and implementation of a scalable, modular, and reproducible platform (\acl{crs}) for building and deploying hybrid conversational recommender agents. The focus is centered on the engineering and architectural challenges inherent in creating a robust, full-stack application-- whereas the complementary research thesis \cite{MUI2ICSI:SOTA} is devoted to the research component and evaluation of the conversational and recommendation components. The specific objectives are detailed as follows.

\begin{objetive}
    \item \textbf{Detailed System Design:} To define and document a resilient and scalable architecture that integrates multiple components, including a frontend user interface, a backend \acs{api} with all the application logic, a \ac{llm} service, and data storage solutions. This architecture will be designed for modularity to facilitate independent development, testing, and deployment of each component.

    \item \textbf{High-Performing Backend Service:} To develop a backend using the FastAPI framework that serves as the backbone of the platform. This includes creating \acs{api} endpoints for managing the lifecycle of recommender agents, handling user interactions, processing data, starting and interacting with conversational workflows and proxying requests to the \ac{llm}.

    \item \textbf{Automated Data Processing Pipeline:} To build a system capable of automatically ingesting, cleaning, and structuring user-provided datasets. This pipeline will standardize heterogeneous data files into a format suitable for both the graph-based recommender and the expert \acs{rs} model, ensuring data integrity and consistency.

    \item \textbf{Responsive Frontend Application:} To build a modern \ac{pwa} using the Next.js framework. This interface will provide users with a comprehensive dashboard to create and manage their recommender agents, as well as an intuitive chat interface to interact with them. Emphasis will be placed on usability, accessibility, and providing a seamless user experience.

    \item \textbf{Scalability and Reproducibility with Containerization:} To utilize Docker to containerize each component of the system (backend, database, \ac{llm} service). This approach will ensure that the entire platform is portable, easy to deploy, and horizontally scalable, adhering to modern DevOps practices.

    \item \textbf{System Testing and Evaluation:} To perform comprehensive testing, including unit and integration tests for backend logic, \acs{api} load testing to measure performance under stress, usability testing with real users, and a comparative analysis of the platform's contributions against established benchmarks or similar systems where applicable.
\end{objetive}
